Towards a Wide-Coverage Grammar for Swedish Using GF

### 2012-01-02 doc/report/report.tex
report: write about generation

The grammar has been extended and enhanced, and its current status is
a specialized extension of the resource grammar. When it comes to parsing,
however, we do not get far without robustness.
The grammar in itself is by no means robust, and just one 
unexpected punctuation mark, unknown word
or missing phrase will cause the parsing of the whole sentence to fail.

>>>>

The grammar has been extended and enhanced, and its current status is
a specialized extension of the resource grammar. When it comes to parsing,
however, we do not get far without robustness.
The grammar in itself is by no means robust, and just one 
unexpected punctuation mark, unknown word
or missing phrase will cause the parsing of the whole sentence to fail. 
Besides parsing, the grammar may well be used for language generation,
which is fast even with an extensive lexicon.
%TODO make nice!
Although it cannot not been verified, we believe that the majority of the
sentences generated are grammatically correct in a syntactical point of view.
Without any semantical knowledge, nonsense phrases cannot be avoided in
random generation. However, an abstract tree has a meaningful interpretation,
the linearization should be correct. There are some cases when the correctness
of the output has been ignored in order to increase the expressivity, such
as ComplBareVV, SupCl. These functions should be excluded or enhanced when doing
careful generation...
``övriga datorer idag som ska vara inte skulle ha målats rödare än johan"
PredVP (DetCN Subject (DetSub oovriga_Det) (RelCN (AdvCN (UseN computer_N) (AdvSub today_Adv)) (UseRCl (TTAnt TFut ASimul) PPos (RelVP IdRP UseCopula)))) (PassVP (SlashV2A paint_V2A (ComparA Object red_A (UsePN Object johan_PN))))

%The use of the NONEXIST pattern, as described in \ref{sec:Formal}. When using
%the grammar for generation, an extra
